Gravitational wave sources in our Galactic backyard: LISA predictions for BH and NS binaries

### 2021-06-09 paper/tex/sections/discussion.tex
lots of results updates, mainly fiducial dists
eccentricity and chirp mass uncertainty
sky localisation

\subsection{Caveats}
\todo{This section is only an outline for now}

\subsubsection{Galaxy Caveats}
\begin{itemize}
    \item Systemic kicks
    \item No models for high $Z$ values in Frankel
    \item No halo or GC considered %GC don't produce NSNS well but other maybe (Kremer+??)
    \item Contribution of metal-poor stars not well known
\end{itemize}

\subsubsection{Detection Caveats}
\begin{itemize}
    \item None come to mind...?
\end{itemize}

@@

>>>>

@@

\subsection{Matching LISA detection to radio pulsars}\label{sec:pulsar_matching}

\subsection{Caveats}\label{sec:caveats}
\todo{This section is only an outline for now}

\subsubsection{Galaxy Caveats}
\begin{itemize}
    \item Systemic kicks
    \item No models for high $Z$ values in Frankel
    \item No halo or GC considered %GC don't produce NSNS well but other maybe (Kremer+??)
    \item Contribution of metal-poor stars not well known
    \item COMPAS models for naked helium stars are based on a single metallicity -- may be why NSNS rate is less dependent on MSSFR
\end{itemize}

\subsubsection{Detection Caveats}
\begin{itemize}
    \item Eccentricity uncertainty is pessimistic (doesn't actually seem to be the dominant problem)
\end{itemize}

### 2021-06-09 paper/tex/sections/results.tex
sky localisation

\subsubsection{Angular resolution}

>>>>

\subsubsection{Sky localisation}
We quantify the sky localisation of a source by calculating its angular resolution. Since we find that all potential sources are stationary on the timescale of the LISA mission, following \citet{Mandel+2018}, we can use the timing accuracy of LISA and the effective detector baseline to calculate the angular resolution, $\sigma_{\theta}$, as
\begin{equation}
    \sigma_{\theta} = 16.6^\circ \left(\frac{7}{\rho}\right) \left(\frac{5 \times 10^{-4} \unit{Hz}}{f_{\rm dom}}\right) \left( \frac{2 \unit{AU}}{L} \right),
\end{equation}
where $\rho$ is the signal-to-noise ratio, $f_{\rm dom}$ is the harmonic frequency with the strongest signal-to-noise ratio ($f_{\rm dom} = n_{\rm dom} f_{\rm orb}$ and $n_{\rm dom} = 2$ for circular binaries) and $L$ is the effective detector baseline.

We plot the angular resolution in the last panel of Fig.~\ref{fig:fiducial_pdf_distributions} as a CDF normalised to the expected detection rate of each DCO. From this plot, we see that many sources can only be resolved to a patch with an area in excess of 100 square degrees \todo{make this positive}. The size of a pencil beam for a 15m diameter SKA dish observing at 1.4 GHz is roughly 0.67 square degrees, corresponding to an angular resolution of $\sigma_\theta = \sqrt{(0.67 / \pi)} = 0.46^\circ$ (approximately the angular size of the moon). Applying this to the plot shows that about 20\% of DCOs can be covered by a single pointing of SKA. We will discuss the prospects of matching LISA detections to radio pulsars with SKA further in Sec.~\ref{sec:pulsar_matching}.
